Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-08 supp.rnw
Add an explanatory comment to the order_species function in the supplementary.
Its not otherwise clear what it's for.

<<echo=FALSE>>=
	order_species <- function(vec, names, order) {
		factor(vec, levels = names[order])
	}

>>>>

<<echo=FALSE>>=
	order_species <- function(vec, names, order) {
		#Takes a vector of species names and redefines them as a factor with correctly ordered levels.
		#This forces ggplot to use them in the correct order for a facet plot.
		factor(vec, levels = names[order])
	}
